SNP Analysis

### 2020-01-08 Paper_resubmit.Rmd
...

p11Loss %>% filter(value <= -1) %>% group_by(Status) %>% tally(name='p11 Loss') %>% 
  full_join( p11 %>% group_by(Status) %>% tally(name='Total Samples') ) %>% 
  kable(caption='Chr17 p11 loss') %>% kable_styling(full_width = F)

@@

legend = get_legend(p)
p = p + theme(legend.position = 'none')

@@

grid.arrange(arrangeGrob(p,p1,p2,nrow=1), arrangeGrob(legend), heights=c(4,1))

ggsave(filename='plots/performance/training_n_pts.png',
       plot=grid.arrange(arrangeGrob(p,p1,p2,nrow=1), arrangeGrob(legend), heights=c(4,1)), width=12, height=8, units='in', dpi=300)

>>>>

p11Loss %>% group_by(Status) %>% tally(name='p11 Loss') %>% 
  full_join( p11 %>% group_by(Status) %>% tally(name='Total Samples') ) %>% 
  kable(caption='Chr17 p11 loss') %>% kable_styling(full_width = F)

@@

legend = cowplot::get_legend(p)
p = p + theme(legend.position = 'none')

@@

grid.arrange(arrangeGrob(p,p1,p2,ncol=1), arrangeGrob(legend), heights=c(4,1))

ggsave(filename='plots/performance/training_n_pts.png',
       plot=grid.arrange(arrangeGrob(p,p1,p2,ncol=1), arrangeGrob(legend), heights=c(6,1)), width=8, height=12, units='in', dpi=300)

### 2020-01-08 snp/SNP_Prediction_Analysis.Rmd
...

Despite that, we still see a fairly consistent high/low risk prediction for NP vs P.  However, HGD in NP patients predicts at a rate consistent with progression.
```{r echo=F}
preds = preds %>% mutate(Pathology = factor(Pathology, levels=c('NDBE','ID','LGD','HGD','EAC'), ordered = T))
rp = plot.risk.by.path(preds) 
rp

@@

```{r, warning=F, fig.height=8}
prog = filter(pred.qc, Status == 'P')
p1 = ggplot(prog, aes(Prob)) + facet_wrap(~Timepoint, scales='free_y',nrow=1) + 
  geom_histogram(aes(fill=..x..), breaks=seq(0,1,0.1) , show.legend = F) +
  scale_fill_gradientn(colors = myPal,  name='') + 
  labs(title='Predictions on progressors', y='n Samples', x='Unadjusted Probability') + theme(text=element_text(size=12))

nonprog = subset(pred.qc, Status == 'NP')
p2 = ggplot(nonprog, aes(Prob)) + facet_wrap(~Timepoint, scales='free_y', nrow=1) + 
  geom_histogram(aes(fill=..x..), breaks=seq(0,1,0.1) , show.legend = F) +
  scale_fill_gradientn(colors = myPal,  name='') + 
  labs(title='Predictions on non-progressors', y='n Samples', x='Unadjusted Probability') + theme(text=element_text(size=12))

@@

p3 = ggplot(normals, aes(Prob)) + facet_wrap(~Type, ncol=2, scales = 'free') +
  geom_histogram(aes(fill=..x..), breaks=seq(0,1,0.1) , show.legend = F) +
  scale_fill_gradientn(colors = myPal,  name='') +
  labs(title='Predictions on Blood/Gastric normals', y='n Samples', x='Unadjusted Probability') + theme(text=element_text(size=12))

>>>>

Despite that, we still see a fairly consistent high/low risk prediction for NP vs P.  However, HGD in NP patients predicts at a rate consistent with progression.
```{r echo=F}
preds = preds %>% mutate(Pathology = factor(Pathology, levels=c('NDBE','ID','LGD','HGD','EAC'), ordered = T))
rp = plot.risk.by.path(preds) + labs(y='% Classified', title='Samples classified by pathology')
rp

@@

```{r, warning=F, fig.height=8}
prog = filter(pred.qc, Status == 'P')
p1 = ggplot(prog, aes(Prob)) + facet_wrap(~Timepoint, scales='free_y',nrow=1) + 
  geom_histogram(aes(fill=..x..), breaks=seq(0,1,0.1) , show.legend = F) +
  scale_fill_gradientn(colors = myPal,  name='') + 
  labs(title='Progressor BE', y='n Samples', x='Unadjusted Probability') + theme(text=element_text(size=12))

nonprog = subset(pred.qc, Status == 'NP')
p2 = ggplot(nonprog, aes(Prob)) + facet_wrap(~Timepoint, scales='free_y', nrow=1) + 
  geom_histogram(aes(fill=..x..), breaks=seq(0,1,0.1) , show.legend = F) +
  scale_fill_gradientn(colors = myPal,  name='') + 
  labs(title='Non-Progressor BE', y='n Samples', x='Unadjusted Probability') + theme(text=element_text(size=12))

@@

p3 = ggplot(normals, aes(Prob)) + facet_wrap(~Type, ncol=2, scales = 'free') +
  geom_histogram(aes(fill=..x..), breaks=seq(0,1,0.1) , show.legend = F) +
  scale_fill_gradientn(colors = myPal,  name='') +
  labs(title='Blood/Gastric Normals', y='n Samples', x='Unadjusted Probability') + theme(text=element_text(size=12))
